%-------------------------
% Resume in Latex
% Author : Shubhang Mishra
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.8in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    {\Huge \scshape Shubhang Mishra} \\ \vspace{0.5pt}
    Greater Noida, Uttar Pradesh, India - 201310 \\ \vspace{0.5pt}
    \small \raisebox{-0.0\height}\faPhone\ +91-7654025369 ~ \href{mailto:shubhangmishra5@gmail.com}{\raisebox{-0.0\height}\faEnvelope\  \ shubhangmishra5@gmail.com} ~ \href{https://www.linkedin.com/in/shubhang-mishra-b7b1181b2/
}{\raisebox{-0.0\height}\faLinkedin\ \ Shubhang Mishra}  ~
    \href{https://github.com/Shubhangmishra5}{\raisebox{-0.0\height}\faGithub\ \ Shubhangmishra5}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {ITS Engineering College, Greater Noida}{Jul 2022 -- Aug 2025}
      {B.Tech. in AI and ML}{}
     
    \resumeSubheading
      {Priyadarshini Polytechnic, Nagpur}{May 2019 -- Jun 2022}
      {Diploma in Electrical Engineering}{}  
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading      
      {Satyam Software Solution Pvt. Ltd.}{Noida}
      {Trainee Engineer }{\textbf{Dec 2024 - Feb 2025}}
      \resumeItemListStart
        \resumeItem{Designed 20+ \textbf{circuits} and 10+ \textbf{PCBs} using \textbf{Altium Designer}, reducing prototyping time by 25\%.  }
        \resumeItem{Debugged 3+ \textbf{R\&D} projects, Resolved 15+ hardware debugging issues, reducing project delays by 30\%. }
      \resumeItemListEnd
    
    
    \resumeSubheading      
      {NewGen IEDC, Greater Noida}{Greater Noida}
      {Project Intern}{\textbf{Jan 2024 - Nov 2024}}
      \resumeItemListStart
        \resumeItem{Led 3+ student teams to develop \textbf{Electronics} and \textbf{IoT} prototype projects in collaboration with 5+ tech experts.}
        \resumeItem{Built 5+ \textbf{IoT} systems using \textbf{Raspberry Pi} and \textbf{Arduino}, integrating \textbf{sensors} and wireless communication for real-time monitoring.}
        \resumeItem{Resolved 15+ cross-domain \textbf{R\&D} challenges (hardware/software) driving 30\% system performance improvements.

}
      \resumeItemListEnd
\resumeSubHeadingListEnd

\vspace{-15pt}
%-----------PROJECTS-----------
\section{Projects}
    \vspace{-7pt}
    \resumeSubHeadingListStart
    \resumeProjectHeading
          {\textbf{Accelerator Enhancer System } $|$ \emph{ \textbf{Raspberry Pi}, \textbf{Python}, \href{https://github.com/Shubhangmishra5/accelerator_enhancer}{\faGithub} }}{Nov 2024}
          \resumeItemListStart
            \resumeItem{Developed an \textbf{Accelerator Enhancer System} with 6 motors, controlled by \textbf{STM32} and \textbf{Raspberry Pi}, with real-time \textbf{Pygame GUI}.  
}
            \resumeItem{Implemented \textbf{3 modes} (Sports, Normal, Eco) for optimizing torque by 35\%.}
                 \resumeItem{Monitored \textbf{Current} (up to 50A) and \textbf{RPM} (up to 100 RPM) in real-time for enhanced system performance.  }
          \resumeItemListEnd 
          \vspace{-13pt}
    \resumeProjectHeading       
          {\textbf{Smart Treadmill} $|$ \emph{Python
  \href{http://github.com/Shubhangmishra5/vfd_modbus}{\faGithub} }} {Jun 2024}
          \resumeItemListStart
            \resumeItem{Designed a \textbf{Raspberry Pi}-based \textbf{smart treadmill} with \textbf{VFD} and \textbf{MQTT} for \textbf{IoT}-enabled real-time control.}
            \resumeItem{Enabled real-time health tracking on 2+ metrics (distance, heart rate) and integrated motor control with 3+ health monitoring features for personalized workouts.

}
            
            
          \resumeItemListEnd 
          \vspace{-20pt}
    \resumeProjectHeading       
          {\textbf{Oxygen Generator using microalgae} $|$ \emph{C
  \href{shorturl.at/fqU7Z}{\faGithub} }} {Apr 2024}
          \resumeItemListStart
            \resumeItem{Created an eco-friendly Oxygen Generator using microalgae, deploying 5+ sensors to monitor oxygen levels and environmental pollution. 
}
            \resumeItem{Deployed \textbf{ESP32}-based remote monitoring system with 5+ sensors, enabling real-time analytics across 3+ \textbf{cloud dashboards} (99.8\% uptime). 
}
           
          \resumeItemListEnd 
          \vspace{-17pt}
      \resumeProjectHeading       
          {\textbf{Personal Voice Assistant} $|$ \emph{Python \href{https://github.com/Shubhangmishra5/voice_assistant}{\faGithub} }}{Aug 2023}
          \resumeItemListStart
            \resumeItem{Built a Python-based voice assistant with \textbf{speech recognition} and \textbf{text-to-speech}, handling 10+ voice commands. }
            \resumeItem{Integrated 3+ \textbf{APIs} to handle voice queries and deliver real-time information. }
            \resumeItem{Automated 4+ tasks, including web search, app control, weather info, and system commands. }
          \resumeItemListEnd 
          \vspace{-12pt}
      
    \resumeSubHeadingListEnd

\vspace{-4.6pt}
%-----------ACHIEVEMENTS-------------
\section{Achievements}

      \resumeItemListStart
      
        \resumeItem{\textbf{Finalist} at \textbf{Electrothon 6.0} by \textbf{NIT Hamirpur}; won \textbf{Orkes} Challenge and Scavenger Hunt.}       
        \resumeItem{Attained a \textbf{top 15} position in \textbf{Hackaccino}, hosted by \textbf{Bennett University}, demonstrating competitive coding skills.} 
        \resumeItem{Represented \textbf{BigBlare Innovation} at the \textbf{UP International Trade Show 2024}.}
      \resumeItemListEnd
            
    % \resumeSubHeadingListEnd

\vspace{-10.5pt}
%-----------TECHNICAL SKILLS---------------
\section{Technical Skills}
  
        {\textbf{Programming Languages}: Python, C, JavaScript, Embedded C}\\
        {\textbf{Hardware}: Arduino, Raspberry Pi, ESP32, STM32, Sensor Integration, Circuit Design, IoT, BMS}\\
        {\textbf{Tools}: Git, GitHub, VS Code, Arduino IDE,Altium, MQTT}\\
        {\textbf{Databases}: MySQL}\\
        {\textbf{OS}: Windows, LINUX}\\
       

\vspace{-5pt}
%-----------INVOLVEMENT---------------
\section{Leadership or Volunteering}
    \resumeSubHeadingListStart
    \resumeSubheading{IDEATHON 2024}{NewGen IEDC}{Organiser}{\textbf{Jul 2023 -- Aug2023}}

        \resumeSubheading{HackWithDelhi, GL Bajaj}{Greater Noida}{Volunteer for Hackathon}{\textbf{May 2024 -- Jun 2024}}
            
    \resumeSubHeadingListEnd

\end{document}
